%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mohnish Sonsare} \\ \vspace{1pt}
    \small 612-282-6707 $|$ \href{mailto:sonsa021@umn.edu}{\underline{sonsa021@umn.edu}} $|$ 
    \href{https://linkedin.com/in/mohnishsonsare}{\underline{linkedin.com/in/mohnish}} $|$
    \href{https://github.com/mohnishc14}{\underline{github.com/mohnish}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Minnesota}{Minneapolis, MN}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- Dec 2025}
    \resumeItem{Relevant Coursework: Program Design \&  Development, Machine Architecture, Statistical Regression, ML Optimization, Advanced Programming Principles}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant (\href{https://grouplens.org}{\textit{GroupLens.org}})}{Jan 2024 -- Present}
      {University of Minnesota, Twin Cities}{Minneapolis, MN}
      \resumeItemListStart
        \resumeItem{Wrote code in a team of three in the development of an interactive tool aimed at making virtual meetings more inclusive using Jitsi, React, Sequelize, and Express.js.}
        \resumeItem{Assisted in developing logic for API calls to enhance interactivity with a chat bot.}
        \resumeItem{Added endpoints and components with comprehensive unit integration testing.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Undergraduate Teaching Assistant}{Sept 2023 -- Present}
      {University of Minnesota, Twin Cities}{Minneapolis, MN}
      \resumeItemListStart
        \resumeItem{TA for Introduction to Algorithms and Data Structure (Java). Conducted weekly office hours and led 3+ labs, overseeing 30+ students in each session.}
        \resumeItem{Collaborated with faculty mentors and fellow Teaching Assistants to enhance assessment, lab write-ups, and other educational materials.}
        \resumeItem{Assisted in the grading process, including midterms, to provide constructive feedback to students and contribute to fair and consistent evaluation practices.}
    \resumeItemListEnd

    \resumeSubheading
      {Year Round Student (\href{https://algorithmicthinking.org}{\textit{algorithmicthinking.org}})}{June 2021 -- May 2022}
      {Program in Algorithmic and Combinatorial Thinking}{New Jersey, NY}
      \resumeItemListStart
        \resumeItem{Received a full tuition scholarship for a year-long selective program on mathematical foundations of computer science by Dr. Rajiv Gandhi at Rutgers Camden and UPenn.}
        \resumeItem{Studied topics in discrete mathematics and explored theoretical and fundamental topics in probability, set theory, advanced permutations and combinations, and linearity of expectation.}
        \resumeItem{Learned about fields of computer science including computational geometry, cryptography, the probabilistic method, and planar graph coloring from guest speakers.}
      \resumeItemListEnd

      \resumeSubheading
      {Summer Student (\href{https://ai-4-all.org}{\textit{AI4ALL}})}{May 2021 -- June 2022}
      {University of Maryland, College Park}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Worked on a \href{https://sites.google.com/umd.edu/ai4allproject-showcase2021/attack} {\textit{research project}}  on how neural networks can be trained to avoid adversarial attacks. }
        \resumeItem {Presented the advantages of an adversarially-trained robust model over a standard model to UMD faculty and students.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Drone Delivery Simulation Model} $|$ \emph{C++, TypeScript, Node.js, Docker}}{Jan 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Collaborated with a teammate in biweekly sprints to develop a data collection model to track drone speed, distance travelled, and delivery time to optimize drone delivery routes.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Leadership}
\resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Secretary, Competitive Programming Club} (\href{https://cpp.umn.edu}{\textit{umncpp.org}})} {Mar 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Moderated a Discord community of 700 members, documented detailed meeting minutes, and regularly updated the club’s website.}
            \resumeItem{Trained students in ICPC problem-solving, participated in competitive coding competitions, honed algorithm skills, and practiced on Kattis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS, x86, OCaml, R} \\
     \textbf{Frameworks}{: React, Node.js,, JUnit, WordPress, GTest Suite} \\
     \textbf{Developer Tools}{: Git, Docker, Jira,  VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
